Multiple quantum NMR in solids as a method of a determination of Wigner--Yanase skew information

### 2021-02-19 manuscript.tex
Rename figure of entangled spins number in nanopore
Add figure of entangled spins number in zigzag

\begin{figure}
	\includegraphics[width=0.95\linewidth]{entangled_spins_by_temp}
	\caption{
		The dependence of the number of the entangled spins on the inverse temperature $\beta = \frac{\pi \omega_0}{kT}$;
		black circles - the results are obtained with the Fisher information;
		open circles - the results are obtained with the Wigner--Yanase information.
	}
	\label{fig:2}
\end{figure}

@@

We investigated the many-spin entanglement in the spin system, consisting of 201 spins, in a nanopore both with
the Wigner--Yanase information $I_{WY}\left(\rho(\tau, \beta), I_z\right)$
and the Fisher information $I_F\left(\rho(\tau,\beta),I_z\right)$.
In Fig.~(\ref{fig:2})the dependence of the number of entangled spins on the inverse temperature is presented.
Fig.~(\ref{fig:2}) demonstrates that the number of the entangled spins increases when the temperature decreases both for the Wigner--Yanase information and the Fisher information.

The analogous investigation was conducted on the model of the proton zigzag chain in a single crystal of hambergite~\cite{23}.
Here the close results on the many--spin entanglement were obtained for both used informations for the system consisting of $6\div 12$ spins~\cite{15}.

>>>>

\begin{figure}
	\includegraphics[width=0.95\linewidth]{nanopora_entangled_spins_by_temp}
	\caption{
		The dependence of the number of the entangled spins on the inverse temperature $\beta = \frac{\pi \omega_0}{kT}$;
		black circles - the results are obtained with the Fisher information;
		open circles - the results are obtained with the Wigner--Yanase information.
	}
	\label{fig:2}
\end{figure}

\begin{figure}
	\includegraphics[width=0.95\linewidth]{zigzag_entangled_spins_by_temp}
	\caption{
		The dependence of the number $N_\mathrm{ent}$ of the entangled spins on the parameter $b$ (the inverse temperature) for zigzag chains consisting of six spins.
	}
	\label{fig:3}
\end{figure}

@@

We investigated the many-spin entanglement in the spin system, consisting of 201 spins, in a nanopore both with
the Wigner--Yanase information $I_{WY}\left(\rho(\tau, \beta), I_z\right)$
and the Fisher information $I_F\left(\rho(\tau,\beta),I_z\right)$.
In Fig.~(\ref{fig:2}) the dependence of the number of entangled spins on the inverse temperature is presented.
Fig.~(\ref{fig:2}) demonstrates that the number of the entangled spins increases when the temperature decreases both for the Wigner--Yanase information and the Fisher information.

The analogous investigation was conducted on the model of the proton zigzag chain in a single crystal of hambergite~\cite{23}.
In Fig.~\ref{fig:3} the close results on the many--spin entanglement for both used informations for the system consisting of $6\div 12$ spins is presented.~\cite{15}.
